---
title: "Explore how mutations enable new binding capabilites"
author: "Tyler Starr"
date: "04/15/2021"
output:
  github_document:
    toc: true
    html_preview: false
editor_options: 
  chunk_output_type: inline
---


```{r setup, message=FALSE, warning=FALSE, error=FALSE}
require("knitr")
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))

#list of packages to install/load
packages = c("yaml","data.table","tidyverse","gridExtra","egg","ggseqlogo")
#install any packages not already installed
installed_packages <- packages %in% rownames(installed.packages())
if(any(installed_packages == F)){
  install.packages(packages[!installed_packages])
}
#load packages
invisible(lapply(packages, library, character.only=T))

#read in config file
config <- read_yaml("config.yaml")

#make output directory
if(!file.exists(config$evolvability_dir)){
  dir.create(file.path(config$evolvability_dir))
}
```
Session info for reproducing environment:
```{r print_sessionInfo}
sessionInfo()
```

## Setup

Read in tables of per-mutant and per-homolog phenotypes. Set some factors for ordering backgrounds and sites.

```{r input_data}
dt_mutant <- data.table(read.csv(config$final_variant_scores_mut_file),stringsAsFactors=F)
#order target by order given in config
dt_mutant$target <- factor(dt_mutant$target,levels=config$mutated_targets_ordered)
#order mutant as a factor for grouping by rough biochemical grouping
dt_mutant$mutant <- factor(dt_mutant$mutant, levels=c("C","P","G","V","M","L","I","A","F","W","Y","T","S","N","Q","E","D","H","K","R"))
#order sites as a factor variable
dt_mutant$position <- factor(dt_mutant$position,levels=c(455,486,493,494,498,501))

dt_wt <- data.table(read.csv(config$final_variant_scores_wt_file),stringsAsFactors=F)
#assign target as a factor in my desired overall plotting order
dt_wt[,target := factor(dt_wt$target,levels=config$targets_ordered)]

```

## Mutation effect jitter plots

Want to make plots that have a bar at the WT binding affinity, and jitter plot for the binding of single-mutant variants.

```{r jitter_huACE2, fig.width=5, fig.height=4, fig.align="center",dpi=300,dev="png"}

p1 <- ggplot(dt_mutant,aes(x=target,y=huACE2))+
  geom_jitter(width=0.1, alpha=0.3)+
  xlab("RBD")+ylab("-log10KD,app (huACE2)")+
  geom_crossbar(aes(ymin=huACE2,ymax=huACE2,width=0.5,fatten=5), data=dt_mutant[position==493 & wildtype_indicator=="x",],color="red")+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90,vjust=0.5,hjust=1))
p1

invisible(dev.print(pdf, paste(config$evolvability_dir,"/huACE2_mutant-jitter.pdf",sep=""),useDingbats=F))
```


Put all together in one faceted plot

```{r jitter_facet_by_ACE2, fig.width=10, fig.height=5, fig.align="center",dpi=300,dev="png"}
#mutate to longform
temp <- data.table::melt(dt_mutant[, .(target,position,mutant,huACE2,cvACE2,pgACE2,mACE2,RaACE2.787,RaACE2.9479,RsACE2.3364,RsACE2.1434,wildtype_indicator)],id.vars=c("target","position","mutant","wildtype_indicator"),measure.vars=c("huACE2","cvACE2","pgACE2","mACE2","RaACE2.787","RaACE2.9479","RsACE2.3364","RsACE2.1434"),variable.name="ACE2",value.name="log10Ka")

p1 <- ggplot(temp,aes(x=target,y=log10Ka))+
  geom_jitter(width=0.1, height=0, alpha=0.3, shape=16)+
  xlab("RBD")+ylab("-log10KD,app")+
  geom_crossbar(aes(ymin=log10Ka,ymax=log10Ka,width=0.6,fatten=4), data=temp[position==493 & wildtype_indicator=="x",],color="red")+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90,vjust=0.5,hjust=1))+
  facet_wrap(~ACE2,nrow=1)+coord_flip()+
  scale_x_discrete(limits = rev(levels(temp$target)))
  
p1

invisible(dev.print(pdf, paste(config$evolvability_dir,"/jitters_facet_by_ACE2.pdf",sep=""),useDingbats=F))
```

Make donut charts to show the fraction of RBDs that bind as WT, bind only as mutant, or no observed binding

```{r donut_binding, fig.width=20, fig.height=5, fig.align="center",dpi=300,dev="png"}
donut_dt <- data.table(category=c("WT binds","only mut binds","no mut binds"), huACE2=c(10/14,2/14,2/14), cvACE2=c(2/14,7/14,5/14), pgACE2=c(7/14,2/14,5/14), mACE2=c(7/14,5/14,2/14), RaACE2.787=c(8/14,4/14,2/14), RaACE2.9479=c(11/14,1/14,2/14), RsACE2.3364=c(4/14,8/14,2/14), RsACE2.1434=c(3/14,5/14,6/14))

# ACE2x <- "mACE2"
# sum(temp[ACE2==ACE2x & position==493 & wildtype_indicator=="x",.(log10Ka)]>6)
# temp[temp[ACE2==ACE2x & mutant!="C", .I[which.max(log10Ka)], by=.(target)]$V1] #see how many have a mutant >6, subtract # wt above

#mutate to long
donut_dt <- data.table::melt(donut_dt,id.vars=c("category"),measure.vars=c("huACE2","cvACE2","pgACE2","mACE2","RaACE2.787","RaACE2.9479","RsACE2.3364","RsACE2.1434"),variable.name="ACE2",value.name="fraction")

donut_dt[,ymax:=cumsum(fraction),by=.(ACE2)]

donut_dt[,ymin:=0]
for(i in 1:nrow(donut_dt)){
  if(donut_dt[i,category]!="WT binds"){
    donut_dt[i,"ymin"] <- donut_dt[i-1,ymax]
  }
}

ggplot(donut_dt, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category))+
  geom_rect()+
  coord_polar(theta="y")+
  facet_wrap(~ACE2,nrow=1)+
  xlim(c(2,4))+
  theme_void()+
  scale_fill_brewer(palette=1)
  

invisible(dev.print(pdf, paste(config$evolvability_dir,"/donut_binds_by_ACE2.pdf",sep=""),useDingbats=F))
```
