---
title: "Isogenic ACE2 titration experiments for predictions and validations"
output:
  github_document:
    html_preview: false
editor_options:
  chunk_output_type: inline
---

```{r setup, message=FALSE, warning=FALSE, error=FALSE}
require("knitr")
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))

#list of packages to install/load
packages = c("ggplot2", "data.table", "tidyverse", "dplyr", "broom", "gridExtra")
#install any packages not already installed
installed_packages <- packages %in% rownames(installed.packages())
if(any(installed_packages == F)){
  install.packages(packages[!installed_packages])
}
#load packages
invisible(lapply(packages, library, character.only=T))

#make results directory
if(!file.exists("results")){
 dir.create(file.path("results"))
}


```

### Define colorblind-friendly palette
```{r define_color_palette}
# The palette with grey:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")
# The palette with black
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
                "#0072B2", "#D55E00", "#CC79A7")
```

## Experiment: isogenic binding curves for new RBD genotypes and select ACE2s

### Read in data table with mean bin at each concentration
```{r read_input}
dt <- read.csv(file="data_input_isogenics3.csv", stringsAsFactors=F)
```

### Convert from geomean to log-mean, and use nM concentrations
```{r calculate_expression_values}
dt$mean_PE <- log(dt$geomean_PE)
dt$conc_nM <- 10^9 * dt$conc_M

head(dt, n=5)
```

### Use `broom` to get the results from fitting `nls` model by group. Fit EC50 and hill coefficient
```{r fit_titrations}
nls_broom <- dt %>%
  group_by(protein, genotype) %>%
  do(tidy(nls(mean_PE ~ (a/(1+(EC50/conc_nM)^n))+b,
              data=.,
              start=list(a=6,b=3.5,EC50=1,n=1),
              lower=list(a=3,b=2,EC50=1e-6,n=0.2),
              upper=list(a=9,b=5,EC50=1e3,n=5),
              algorithm="port"
              )
          )
  )

dt <- dt %>%
  merge(nls_broom %>%
          filter(term=="EC50") %>%
          select(estimate, std.error) %>%
          rename(EC50="estimate",
                 EC50_SE="std.error"), by=c("protein","genotype"), sort=F)

dt <- dt %>%
  merge(nls_broom %>%
          filter(term=="n") %>%
          select(estimate, std.error) %>%
          rename(hill="estimate",
                 hill_SE="std.error"), by=c("protein","genotype"), sort=F)

write.csv(nls_broom,"./results/nls_fits_isogenics1.csv", row.names = FALSE)

head(dt, n=5)
```
### Write summary table to CSV file
```{r write_output_table}
summary <- dt %>%
  select(protein, genotype, EC50, EC50_SE, hill, hill_SE) %>%
  unique()

summary
write.csv(summary,"./results/summary_isogenics3.csv", row.names = FALSE)
```

### Now predict `mean_PE` using the models, to plot
```{r predict_y}
conc_nM = c(1:20 %o% 10^(-6:3)) # this should only generate ~200 estimates per titration (faster!)

nls_predictions <- dt %>%
  select(protein, genotype) %>%
  merge(nls_broom %>%
          select(-statistic, -p.value, -std.error) %>%
          spread(term, estimate),
        by=c("protein","genotype"),sort=F) %>%
  unique() %>%
  merge(dt %>% select(protein, genotype, EC50_SE) %>% unique(), by=c("protein","genotype"),sort=F) %>%
  merge(as.data.frame(conc_nM), all=TRUE,sort=F) %>%
  mutate(mean_PE = (a/(1+(EC50/conc_nM)^n))+b)

head(nls_predictions, n=5)
```

### Make plots for titration curves 
```{r plot_titrations, fig.width=12,fig.height=11,fig.align="center", dpi=500,dev="png",message=FALSE,error=FALSE,warning=FALSE}
annotations <- dt %>%
  select(protein, genotype, EC50) %>%
  unique() %>%
  remove_rownames()

ggplot(dt, aes(conc_nM, mean_PE)) +
  geom_point() +
  geom_line(data = nls_predictions,
            aes(conc_nM, mean_PE),
            color="red") + 
  scale_x_log10(lim=c(1e-6,1e3)) +
  xlab("[ACE2] (nM)") +
  ylab("PE MFI") +
  facet_wrap(~ genotype+protein,ncol=6) +
  geom_text(
    data    = annotations,
    mapping = aes(x = 1e-4,
                  y = 10.5,
                  label = c(paste(
                    "EC50=", format(EC50, digits=2),
                    "nM"))),
    size=3) +
  theme_bw()

ggsave(
  "./results/isogenics3.pdf",
  scale = 1,
  width = NA,
  height = NA,
  useDingbats=F
)
```

Make individual subpanels with desired overlapping curves for each genotype across all ACE2s:
```{r plot_titrations_multi1, fig.width=10,fig.height=10,fig.align="center", dpi=500,dev="png",message=FALSE,error=FALSE,warning=FALSE}

p1 <- ggplot(dt %>% filter(genotype %in% c("BtKY72")), aes(conc_nM, mean_PE)) +
  geom_point(aes(color=protein)) +
  geom_line(data = nls_predictions %>% filter(genotype %in% c("BtKY72")),
            aes(conc_nM, mean_PE, color=protein),
            ) + 
  ggtitle("BtKY72") +
  scale_x_log10(lim=c(1e-6,1e3)) +
  scale_y_continuous(lim=c(2.75,12)) +
  xlab("[ACE2] (nM)") +
  ylab("PE MFI") +
  scale_color_manual(values=cbPalette) +
  theme_bw()

p2 <- ggplot(dt %>% filter(genotype %in% c("PRD-0038")), aes(conc_nM, mean_PE)) +
  geom_point(aes(color=protein)) +
  geom_line(data = nls_predictions %>% filter(genotype %in% c("PRD-0038")),
            aes(conc_nM, mean_PE, color=protein),
            ) +  
  ggtitle("PRD-0038") +
  scale_x_log10(lim=c(1e-6,1e3)) +
  scale_y_continuous(lim=c(2.75,12)) +
  xlab("[ACE2] (nM)") +
  ylab("PE MFI") +
  scale_color_manual(values=cbPalette) +
  theme_bw()

p3 <- ggplot(dt %>% filter(genotype %in% c("PDF-2370")), aes(conc_nM, mean_PE)) +
  geom_point(aes(color=protein)) +
  geom_line(data = nls_predictions %>% filter(genotype %in% c("PDF-2370")),
            aes(conc_nM, mean_PE, color=protein),
            ) +  
  ggtitle("PDF-2370") +
  scale_x_log10(lim=c(1e-6,1e3)) +
  scale_y_continuous(lim=c(2.75,12)) +
  xlab("[ACE2] (nM)") +
  ylab("PE MFI") +
  scale_color_manual(values=cbPalette) +
  theme_bw()

p4 <- ggplot(dt %>% filter(genotype %in% c("PRD-0038+K493Y+T498W")), aes(conc_nM, mean_PE)) +
  geom_point(aes(color=protein)) +
  geom_line(data = nls_predictions %>% filter(genotype %in% c("PRD-0038+K493Y+T498W")),
            aes(conc_nM, mean_PE, color=protein),
            ) +  
  ggtitle("PRD-0038+K493Y+T498W") +
  scale_x_log10(lim=c(1e-6,1e3)) +
  scale_y_continuous(lim=c(2.75,12)) +
  xlab("[ACE2] (nM)") +
  ylab("PE MFI") +
  scale_color_manual(values=cbPalette) +
  theme_bw()

g <- arrangeGrob(p1, p2, p3, p4, ncol=2, widths=c(3.75,3.75), heights=c(2.5,2.5))

ggsave(
  "./results/isogenics3_multi1.pdf",
  g,
  scale = 1,
  width = 7.5,
  height = 5,
  useDingbats=F
)

```
